Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
update

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{algorithm2e}
\usepackage{rotating}
\usepackage[space]{grffile}
\usepackage[font=small,skip=0pt]{caption}
\DeclareMathOperator{\Tr}{Tr}
% Include other packages here, before hyperref.

@@

\subsection{Pose Detection}

@@

We propose a variation of Whitened Histograms of Orientations (WHO) \cite{Hariharan12} that can generate a template in 70ms (compared to several seconds to generate a WHO template) that is more discriminative than WHO. We call this Non-Zero Whitened Histograms of Orientations (NZ-WHO).

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{verbatim}
\usepackage{subcaption}
\usepackage{algorithm2e}
\usepackage{rotating}
\usepackage[space]{grffile}
\usepackage[font=small,skip=0pt]{caption}
%\DeclareMathOperator{\Tr}{Tr}
% Include other packages here, before hyperref.

@@

\subsection{Object Detection and Viewpoint Estimation}

@@

We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO, that are both more discriminative than WHO, and can be generated two orders of magnitude faster. This speedup means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.
